Comparison of three similarity scores for bullet LEA matching\tnoteref{t1}\tnoteref{t2}

### 2019-12-09 index.Rnw
Bandwidth fix

p3 <- all_lands %>% 
  gather(key = "measure", value = "value", ccf, cms, rfscore) %>%
  mutate(measure = factor(measure, levels = c("ccf", "cms", "rfscore"),
                          labels = c("Cross correlation", "CMS", "RF score")),
         study = paste(study, group1) %>% str_trim() %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3"))) %>%
  filter(measure == "CMS") %>%
  ggplot(aes(
    x = value, fill = sameland,
    colour = sameland
  )) +
  geom_density(alpha = 0.6) +
#  geom_rug(alpha = 0.5/12, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("Land-to-Land scores") +
  theme(legend.position = "bottom", axis.text.y = element_text(hjust = .5, angle = 90)) +
  geom_hline(yintercept = 0, show.legend = F)

>>>>

p3data <- all_lands %>% 
  gather(key = "measure", value = "value", ccf, cms, rfscore) %>%
  mutate(measure = factor(measure, levels = c("ccf", "cms", "rfscore"),
                          labels = c("Cross correlation", "CMS", "RF score")),
         study = paste(study, group1) %>% str_trim() %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3"))) %>%
  filter(measure == "CMS")
p3bw <- bw.nrd0(p3data$value[p3data$sameland & p3data$study == "Houston FSI G1"])
p3 <- ggplot(p3data, aes(
    x = value, fill = sameland,
    colour = sameland
  )) +
  geom_density(alpha = 0.6, bw = p3bw) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("Land-to-Land scores") +
  theme(legend.position = "bottom", axis.text.y = element_text(hjust = .5, angle = 90)) +
  geom_hline(yintercept = 0, show.legend = F)
